---
title: 'Beta/Variance Report'
author: "Steve and Jonathan"
date: " `r as.Date(Sys.time())` "
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_depth: 3
    toc_float: yes
---




```{r setup, include=FALSE, cache=FALSE}
knitr::opts_chunk$set(echo = FALSE
	, warning = FALSE
	, message = FALSE
	, fig.width = 10
	, fig.height = 10
	, results = "asis")
options(width = 12)

library(ggplot2)
theme_set(theme_bw() +
	theme(panel.spacing=grid::unit(0,"lines")))
```

The intercept variance is taken to be zero ($\beta_0 = 0$) hence in all simulations, the regressions will give the same predictions at $x = 0$. The variance in the slope ($\beta_1 = 1$) is taken to be $1$ and $\beta_z \in \{1,2,3,4,5\}$. On the logit-scale, as the variance of $\beta_z$ increases, the predicted probabilities increase with a positive or negative values. Similar trend is observed in the probability-scale plot. However, as the $\beta_z$ increase, the relations between the predictions and $x$ becomes more linear. 

## Logit-scale plot

```{r, echo = FALSE}
load("binary_random.rda")
print(pplot_logit)
```

## Probability-scale plot

```{r, echo = FALSE}
print(pplot_prob)
```
