---
title: 'Analysis of simulated data documentation'
author: "Steve and Jonathan"
date: " `r as.Date(Sys.time())` "
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_depth: 3
    toc_float: yes
---




```{r setup, include=FALSE, cache=FALSE}
knitr::opts_chunk$set(echo = FALSE
	, warning = FALSE
	, message = FALSE
	, fig.width = 10
	, fig.height = 10
	, results = "asis")
options(width = 12)

library(DT)
library(data.table)
library(ggplot2)
library(tibble)
library(tidyr)
library(dplyr)
library(rstanarm)
library(broom)

theme_set(theme_bw() +
	theme(panel.spacing=grid::unit(0,"lines")))

load("simulateHierarchicalmvn.rda")
load("rstanarmModelbin.rda")
```

# Data

The data is simulated as per the writeup [here](https://cygubicko.github.io/wash/simulations_writeup.html), except that $\beta_k$, $k = 1,2,3$ are fixed. 

* It has `r length(unique(sim_dflist[[1]]$hhid))` households per year repeatedly collected for `r length(unique(sim_dflist[[1]]$years))` years.


```{r}
sims_df <- (sim_dflist[[1]]
	%>% filter(hhid %in% sample(hhid, 5))
	%>% mutate_at(c("y1", "y2", "y3", "wealthindex"), function(y){round(y, 3)})
	%>% datatable(caption = "Simulated dataset", rownames = FALSE)
)
sims_df
```

# Analysis

We use Bayesian multivariate generalized linear models with correlated group-specific terms via Stan to model the binary outcomes

* Random intercept model: Assume an intercept that is different for each year
* Jointly simulated $\epsilon_{ik}$ with $\mu_k = \mathbf{0}$ and covariance $\mathbf{\Sigma}$

In other words, the fitted model was specified as:

\[y_{ijk} = \beta0_{jk} + \beta1_kx_i + \epsilon_{ik}\]

		model <- stan_mvmer(
			formula = list(
				y1bin ~ wealthindex + (1 | years)
				, y2bin ~ wealthindex + (1 | years)
				, y3bin ~ wealthindex + (1 | years)
			)
			, data = sim_dflist[[1]]
			, family = list(binomial, binomial, binomial)
		)

# Results

## Fixed effects

```{r}
# Tidy true betas and sigma
betas_df <- (betas_df
   %>% mutate(coef_clean = coef
		, coef_clean = ifelse(grepl("0$", coef_clean), paste0("y", substr(n, 1, 1), "|(Intercept)")
         , ifelse(grepl("x:y[1-9]", coef_clean), paste0("y", substr(n, 1, 1), "|wealthindex")
            , ifelse(grepl("_sd", coef_clean), paste0("sd_y", n, "|(Intercept).years")
            	, ifelse(grepl("^cor_", coef_clean), paste0("cor_y", substr(n, 1, 1), "|(Intercept).y", substr(n, 2, 2), "|(Intercept).years")
						, coef_clean
					)
				)
         )
      )
   )
)
rstanmodel <- rstanmodel_list[[1]]
```

```{r}
fixed_effects <- (summary(rstanmodel, regex_pars = "^y[1-3]\\|\\(Intercept\\)|wealthindex")
	%>% round(., digits = 4)
	%>% datatable()
)
fixed_effects
```

```{r}
fixed_effects <- (summary(rstanmodel)
	%>% round(., digits = 4)
	%>% datatable()
)
fixed_effects
```

```{r}
#print(plot(rstanmodel, regex_pars = "^y[1-3]\\|\\(Intercept\\)|wealthindex")
#	+ geom_point(data = betas_df %>% filter(grepl("^y[1-3]\\|\\(Intercept\\)|wealthindex", coef_clean))
#		, aes(x = betas, y = coef_clean), colour = "red"
#	)
#)
print(plot(rstanmodel, "dens", regex_pars = "^y[1-3]\\|\\(Intercept\\)|wealthindex") 
	+ geom_vline(data = betas_df %>% filter(grepl("^y[1-3]\\|\\(Intercept\\)|wealthindex", coef_clean))
		%>% setnames(c("coef_clean", "betas"), c("Parameter", "Value"))
		, aes(xintercept = Value)
		, linetype = "dashed"
		, colour = "red"
	)
   + facet_wrap(~Parameter, scales = "free", ncol = 3)
	+ theme(strip.text.x = element_text(size = 6))
)
```

## Year-specific estimates

```{r}
#plot(rstanmodel, "mcmc_areas", pars = "varying")
plot(rstanmodel, regex_pars = "^b\\[y[1-3]\\|\\(Intercept\\) years:")
```

## HH-specific estimates

```{r}
plot(rstanmodel, regex_pars = "^b\\[y[1-3]\\|\\(Intercept\\) hhid:")
```

## Covariance and Sigma

```{r}
#plot(rstanmodel, "mcmc_areas", pars = "varying")
#summaryTwoLevelModelVar<- tidy(rstanmodel, intervals=TRUE, prob=.95, parameters = "hierarchical")
#datatable(print(summaryTwoLevelModelVar, digits = 2))

true_cor_df <- (betas_df
	%>% filter(grepl("cor_|_sd", coef))
	%>% mutate(Parameter = gsub("years", "hhid", Parameter))
	%>% rbind(., filter(betas_df, grepl("cor_|_sd", coef)))
	%>% select(c("Parameter", "Value"))
	%>% setnames(names(.), c("term", "true_value"))
)
cor_tabs <- (tidy(rstanmodel, parameters = "hierarchical")
	%>% right_join(true_cor_df)
	%>% select(c("term", "group", "true_value", "estimate"))
	%>% mutate(diff = round(abs(estimate - true_value), 2))
	%>% datatable(options = list(pageLength = 20), rownames = FALSE)
	%>% formatRound(columns=c("estimate"), digits = 4)
	%>% formatStyle("diff"
		, backgroundColor = styleInterval(0.1, c("lightgreen", "red"))
	)
)
cor_tabs

```


