---
title: 'Simulated data documentation'
author: "Steve and Jonathan"
date: " `r as.Date(Sys.time())` "
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_depth: 3
    toc_float: yes
---




```{r setup, include=FALSE, cache=FALSE}
knitr::opts_chunk$set(echo = FALSE
	, warning = FALSE
	, message = FALSE
	, fig.width = 10
	, fig.height = 10
	, results = "asis")
options(width = 12)

library(DT)
library(ggplot2)
library(tidyr)
library(dplyr)

theme_set(theme_bw() +
	theme(panel.spacing=grid::unit(0,"lines")))

load("additional_summaries.rda")
```

# Data exploration

## Water sources

The table below summarises the distribution of household access to water by interview year. The `0` and `1` columns indicate unimproved and improved water services, respecitvely, while n$\_$hh$\_$int indicates the total number of interviews per household.

* Each household was surveyed only once per year. 
* Some household had either unimproved or improved water services for different years. 

In most slum dwelllings, the services are at times not available throught the year. Hence grouping by the year would be more realistic. Similar trends are observed in other services.

The dataset does not contain individual ID hence it is not easy to figure out whether HH members with different services are the same or different. *Might reach out to Damazo if we can get the individual IDs or dataset with the IDs*

```{r}

watersource_tab <- (watersource_tab$count_df
	%>% arrange(hhid_anon)
	%>% group_by(.dots = c("hhid_anon"))
	%>% mutate(n_hh_int = n())
	%>% datatable(caption = "Water source", rownames = FALSE)
)
watersource_tab
```


```{r}
#wealthindex_hh_tab <- (wealthindex_hh_tab
#	%>% arrange(hhid_anon)
#	%>% group_by(.dots = c("hhid_anon"))
#	%>% select(-prop)
#	%>% mutate(wealthindex = round(wealthindex, 3))
#	%>% mutate(n_hh_int = n())
#	%>% arrange(desc(n))
#	%>% datatable(caption = "Income", rownames = FALSE)
#)
#wealthindex_hh_tab
```

## HH income per interview year

However, if we aggregate HH incomes by year, all households had different incomes (`equal_income = ` `r sum(wealthindex_tab$n>1, na.rm = TRUE)`).

* Grouped by hh and year, wealth index is different.

```{r}
wealthindex_tab <- (wealthindex_tab
	%>% arrange(hhid_anon)
	%>% group_by(.dots = c("hhid_anon"))
	%>% select(-prop)
	%>% mutate(wealthindex = round(wealthindex, 3))
	%>% mutate(n_hh_int = n())
	%>% arrange(desc(n))
	%>% datatable(caption = "Income", rownames = FALSE)
)
wealthindex_tab
```

# Simulation plan and assumptions

* Use year as the grouping variable
* Each household has its own year effect on the intercepts and slopes (random-intercept and random-slope)
<!-- * Use average income per household, adjusted by the HH size (total number of people in the HH) as the predictor (any opinion or suggestion on this?). -->

Consider the model
\[y_{ijk} = \beta0_{jk} + \beta1_{jk}x_i + \epsilon_{ik}\]

* $y_{ijk}$ is the simulated value of the ith household in the jth year of the kth service; $i$ goes from 1 to the number of households; $j = 1,2, \cdots, 15$ indexes the number of years and we consider equal number of households per year; and $k = 1, 2, 3$ indexes the number of services. We therefore simulate three services $y_1, y_2$ and $y_3$.
* $\beta0_{jk}$ is the random-intercept effect of the jth year of the kth service on the response. We assume $\beta0_{jk} \sim MVN(\mu0_k, \Sigma_{tk})$; $t = 1, 2, 3$.
* $\beta1_{jk}$ is the random-slope effect of the jth year of the kth service on the response. We assume $\beta1_{jk} \sim MVN(\mu1_k, \Sigma_{tk})$.
* $\epsilon_{ik}$ is the household-level random effect (residual error term) of the kth service. We assume $\epsilon_{ik} \sim N(0, 1).$
* $x_j$ is the ith predictor value.

We convert $y_{ijk}$ to binary scale by drawing samples from a binomial distribution, with probability, $p_k = plogis(y_{ijk})$.

